\bf Title here

### 2020-07-20 paper/paper.Rmd
tweaks on the definition of global object, mainly notation

If we are being pedantic, all the target bases, except the starting basis, should have a searching index since it is the last candidate basis that successfully allows the optimisation algorithm to end and output a new basis for interpolation. If we denotes the length of each search (number of basis searched in each iteration) as $l_1, l_2, \cdots, l_J$ and the length of each interpolation is $k_1, k_2, \cdots, k_J$ , then the searching index for target basis in each iteration will become $l_1, l_1 + l_2, \cdots, l_1 +l_2+\cdots l_J$. To avoid this complex notation involving opteration in the subscript, we simplify it using a superscript as $$\mathbf{A}^{0}, \mathbf{A}^{1}, \mathbf{A}^{2}, \cdots, \mathbf{A}^{J}$$ where $\mathbf{A}^{0}$ is the starting basis. Notice that in the case when the complex notation can't be avoided, we shall separate each index using a comma and  write the index in brackets if necessary. Using the notation above, all the bases on the interpolation path (including target and interpolation bases) can be written as in Equation \ref{eq:interp-path}.

@@

## Origin idea
<!-- Visual diagnostics can be real-time or post-run. Real time diagnostic directly uses the data produced in the algorithm to produce visual representation and thus doesn't need to store the data.   This section focuses on the definition and production of post-run diagnostics and the next section discusses real-time diagnostics. -->

@@

Ggplot requires a data frame that contains all the variables to plot and a *global object* is constructed as the data frame supplied to the visual diagnostic plots to better suit the characters of iterative optimisation algorithms. Given an optimisation algorithm, two primary variables of interest are the *decision variable: $\mathbf{A}$* and the *value of the objective function: $I$*.

*Iterators* indexes the data collected and has a time series feature that prescribes the its natural ordering of the decision varible in the searching. The simpliest iterator, *index per observation: $t$*, is a unique identifier for each observation in the data. For each level of iteration, we design two types of indices: *index per iteration* is fixed for each observations in one iteration and has an increment of one once a new iteration starts. *index within iteration* has an increment of one for each observation in an iteartion and starts over from one once a new iteration starts. A sketch of the difference between these three iterators is provided in Figure \ref{iterators}.

@@

In projection pursuit optimisation algorithms, there is one level of iteartion and hence exists three iterators: `id` indices each observation by a unique number; `tries` is the index per iteration iterator that gets updated once a search-and-interpolate step is finished; and `loop` is the index within iteration iterator and starts over from one at the beginning of a new `tries`.

There could exist other parameters that are also of our interest but can't be classified as one of the three categories. They are defined under the fourth category: *other parameter of interest: $S$*. In projection pursuit, three other parameters of our interest includes `method`, `alpha` and `info`.  `method` identifies the name of the searching method used and we are interested in comparing the performance between different algorithms under direct search. The neighbourhood parameter `alpha` controls the size of the sampling space and we are interested to understand how the searching space shrinks as the algorithm progresses. `info` labels different stages in the searching process. A sketch of the global object for projection pursuit guided tour is presented in Figure \ref{fig:glb-obj}.

@@

To write down the notation for the data structure, it is easier to write the bases as a column vector denoting by a single subscript by their natural ordering:

where $T$ is the total number of plane serached by the optimisation algorithm including all the target planes, all the interpolating planes and all the candidate planes but NOT the starting plane. The full data structure can thus be shown as in Equation \ref{eq:data-structure}.

>>>>

If we are being pedantic, all the target bases, except the starting basis, should have a searching index since it is the last candidate basis that successfully allows the optimisation algorithm to end and output a new basis for interpolation. If we denotes the length of each search (number of basis searched in each iteration) as $l_1, l_2, \cdots, l_J$ and the length of each interpolation is $k_1, k_2, \cdots, k_J$ , then the searching index for target basis in each iteration will become $\mathbf{A}_{1l_1*}, \mathbf{A}_{2l_2*}, \cdots, \mathbf{A}_{Jl_J*}$. We simplify this notation for target bases by using a superscript as $$\mathbf{A}^{0}, \mathbf{A}^{1}, \mathbf{A}^{2}, \cdots, \mathbf{A}^{J}$$ where $\mathbf{A}^{0}$ is the starting basis. Notice that in the case when the complex notation can't be avoided, we shall separate each index using a comma and  write the index in brackets if necessary. Using the notation above, all the bases on the interpolation path (including target and interpolation bases) can be written as in Equation \ref{eq:interp-path}.

@@

## Motivation
<!-- Visual diagnostics can be real-time or post-run. Real time diagnostic directly uses the data produced in the algorithm to produce visual representation and thus doesn't need to store the data.   This section focuses on the definition and production of post-run diagnostics and the next section discusses real-time diagnostics. -->

@@

Ggplot requires a data frame that contains all the variables to plot and a *global object* is constructed as the data frame supplied to the visual diagnostic plots to better suit the characters of iterative optimisation algorithms. Given an optimisation algorithm, two primary variables of interest are the *decision variable: $\mathbf{A}$* and the *value of the objective function: $I$*. To further simplify the notation for $\mathbf{A}$, we write the bases as a column vector denoting by a single subscript by their natural ordering as in Equation \ref{vector-basis}.

where $T$ is the total number of plane serached by the optimisation algorithm including all the target planes, all the interpolating planes and all the candidate planes but NOT the starting plane.

*Iterators* indexes the data collected and has a time series feature that prescribes the its natural ordering of the decision varible in the searching. The simpliest iterator, *index per observation: $t$*, is a unique identifier for each observation in the data. For each level of iteration, we design two types of indices: *index per iteration: $j$* is fixed for each observations in one iteration and has an increment of one once a new iteration starts. *index within iteration: $l$* has an increment of one for each observation in an iteartion and starts over from one once a new iteration starts. A sketch of the difference between these three iterators is provided in Figure \ref{iterators}. In projection pursuit optimisation algorithms, there is one level of iteartion and hence exists three iterators: `id` indices each observation by a unique number; `tries` is the index per iteration iterator that gets updated once a search-and-interpolate step is finished; and `loop` is the index within iteration iterator and starts over from one at the beginning of a new `tries`. We give the interpolating basis a different index $k$ for projection pursuit guided tour. It is similar in nature to $l$ but is specific for interpolating bases, which is usually not part of the optimisation.

@@

There could exist other parameters that are also of our interest but can't be classified as one of the three categories. They are defined under the fourth category: *other parameter of interest: $S$*. In projection pursuit, three other parameters of our interest includes `method`, `alpha` and `info`.  `method` identifies the name of the searching method used and we are interested in comparing the performance between different algorithms under direct search. The neighbourhood parameter `alpha` controls the size of the sampling space and we are interested to understand how the searching space shrinks as the algorithm progresses. `info` labels different stages in the searching process. A sketch of the global object for projection pursuit guided tour is presented in Figure \ref{fig:glb-obj}. The full data structure can thus be shown as in Equation \ref{eq:data-structure}.

@@

### 2020-07-20 paper/paper.tex
tweaks on the definition of global object, mainly notation

If we are being pedantic, all the target bases, except the starting
basis, should have a searching index since it is the last candidate
basis that successfully allows the optimisation algorithm to end and
output a new basis for interpolation. If we denotes the length of each
search (number of basis searched in each iteration) as
\(l_1, l_2, \cdots, l_J\) and the length of each interpolation is
\(k_1, k_2, \cdots, k_J\) , then the searching index for target basis in
each iteration will become
\(l_1, l_1 + l_2, \cdots, l_1 +l_2+\cdots l_J\). To avoid this complex
notation involving opteration in the subscript, we simplify it using a
superscript as
\[\mathbf{A}^{0}, \mathbf{A}^{1}, \mathbf{A}^{2}, \cdots, \mathbf{A}^{J}\]
where \(\mathbf{A}^{0}\) is the starting basis. Notice that in the case
when the complex notation can't be avoided, we shall separate each index
using a comma and write the index in brackets if necessary. Using the
notation above, all the bases on the interpolation path (including
target and interpolation bases) can be written as in Equation
\ref{eq:interp-path}.

@@

\hypertarget{origin-idea}{%
\subsection{Origin idea}\label{origin-idea}}

@@

Ggplot requires a data frame that contains all the variables to plot and
a \emph{global object} is constructed as the data frame supplied to the
visual diagnostic plots to better suit the characters of iterative
optimisation algorithms. Given an optimisation algorithm, two primary
variables of interest are the \emph{decision variable: \(\mathbf{A}\)}
and the \emph{value of the objective function: \(I\)}.

\emph{Iterators} indexes the data collected and has a time series
feature that prescribes the its natural ordering of the decision varible
in the searching. The simpliest iterator, \emph{index per observation:
\(t\)}, is a unique identifier for each observation in the data. For
each level of iteration, we design two types of indices: \emph{index per
iteration} is fixed for each observations in one iteration and has an
increment of one once a new iteration starts. \emph{index within
iteration} has an increment of one for each observation in an iteartion
and starts over from one once a new iteration starts. A sketch of the
difference between these three iterators is provided in Figure
\ref{iterators}.

@@

In projection pursuit optimisation algorithms, there is one level of
iteartion and hence exists three iterators: \texttt{id} indices each
observation by a unique number; \texttt{tries} is the index per
iteration iterator that gets updated once a search-and-interpolate step
is finished; and \texttt{loop} is the index within iteration iterator
and starts over from one at the beginning of a new \texttt{tries}.

There could exist other parameters that are also of our interest but
can't be classified as one of the three categories. They are defined
under the fourth category: \emph{other parameter of interest: \(S\)}. In
projection pursuit, three other parameters of our interest includes
\texttt{method}, \texttt{alpha} and \texttt{info}. \texttt{method}
identifies the name of the searching method used and we are interested
in comparing the performance between different algorithms under direct
search. The neighbourhood parameter \texttt{alpha} controls the size of
the sampling space and we are interested to understand how the searching
space shrinks as the algorithm progresses. \texttt{info} labels
different stages in the searching process. A sketch of the global object
for projection pursuit guided tour is presented in Figure
\ref{fig:glb-obj}.

@@

To write down the notation for the data structure, it is easier to write
the bases as a column vector denoting by a single subscript by their
natural ordering:

where \(T\) is the total number of plane serached by the optimisation
algorithm including all the target planes, all the interpolating planes
and all the candidate planes but NOT the starting plane. The full data
structure can thus be shown as in Equation \ref{eq:data-structure}.

>>>>

If we are being pedantic, all the target bases, except the starting
basis, should have a searching index since it is the last candidate
basis that successfully allows the optimisation algorithm to end and
output a new basis for interpolation. If we denotes the length of each
search (number of basis searched in each iteration) as
\(l_1, l_2, \cdots, l_J\) and the length of each interpolation is
\(k_1, k_2, \cdots, k_J\) , then the searching index for target basis in
each iteration will become
\(\mathbf{A}_{1l_1*}, \mathbf{A}_{2l_2*}, \cdots, \mathbf{A}_{Jl_J*}\).
We simplify this notation for target bases by using a superscript as
\[\mathbf{A}^{0}, \mathbf{A}^{1}, \mathbf{A}^{2}, \cdots, \mathbf{A}^{J}\]
where \(\mathbf{A}^{0}\) is the starting basis. Notice that in the case
when the complex notation can't be avoided, we shall separate each index
using a comma and write the index in brackets if necessary. Using the
notation above, all the bases on the interpolation path (including
target and interpolation bases) can be written as in Equation
\ref{eq:interp-path}.

@@

\hypertarget{motivation}{%
\subsection{Motivation}\label{motivation}}

@@

Ggplot requires a data frame that contains all the variables to plot and
a \emph{global object} is constructed as the data frame supplied to the
visual diagnostic plots to better suit the characters of iterative
optimisation algorithms. Given an optimisation algorithm, two primary
variables of interest are the \emph{decision variable: \(\mathbf{A}\)}
and the \emph{value of the objective function: \(I\)}. To further
simplify the notation for \(\mathbf{A}\), we write the bases as a column
vector denoting by a single subscript by their natural ordering as in
Equation \ref{vector-basis}.

where \(T\) is the total number of plane serached by the optimisation
algorithm including all the target planes, all the interpolating planes
and all the candidate planes but NOT the starting plane.

\emph{Iterators} indexes the data collected and has a time series
feature that prescribes the its natural ordering of the decision varible
in the searching. The simpliest iterator, \emph{index per observation:
\(t\)}, is a unique identifier for each observation in the data. For
each level of iteration, we design two types of indices: \emph{index per
iteration: \(j\)} is fixed for each observations in one iteration and
has an increment of one once a new iteration starts. \emph{index within
iteration: \(l\)} has an increment of one for each observation in an
iteartion and starts over from one once a new iteration starts. A sketch
of the difference between these three iterators is provided in Figure
\ref{iterators}. In projection pursuit optimisation algorithms, there is
one level of iteartion and hence exists three iterators: \texttt{id}
indices each observation by a unique number; \texttt{tries} is the index
per iteration iterator that gets updated once a search-and-interpolate
step is finished; and \texttt{loop} is the index within iteration
iterator and starts over from one at the beginning of a new
\texttt{tries}. We give the interpolating basis a different index \(k\)
for projection pursuit guided tour. It is similar in nature to \(l\) but
is specific for interpolating bases, which is usually not part of the
optimisation.

@@

There could exist other parameters that are also of our interest but
can't be classified as one of the three categories. They are defined
under the fourth category: \emph{other parameter of interest: \(S\)}. In
projection pursuit, three other parameters of our interest includes
\texttt{method}, \texttt{alpha} and \texttt{info}. \texttt{method}
identifies the name of the searching method used and we are interested
in comparing the performance between different algorithms under direct
search. The neighbourhood parameter \texttt{alpha} controls the size of
the sampling space and we are interested to understand how the searching
space shrinks as the algorithm progresses. \texttt{info} labels
different stages in the searching process. A sketch of the global object
for projection pursuit guided tour is presented in Figure
\ref{fig:glb-obj}. The full data structure can thus be shown as in
Equation \ref{eq:data-structure}.

@@
